Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-02-01 Code/R/RMarkdown/EntropyPlots.Rmd
add size and power analysis and new images

>>>>

<!-- ```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'} -->

<!-- load("./Data/results_gi0_1.Rdata") -->

<!-- mu_values <-c(1, 2) -->

<!-- # Interpretación de rechazo o no rechazo -->
<!-- for (mu_val in mu_values) { -->
<!--   results_data <- results_gi0_1[[as.character(mu_val)]] -->

<!--   table_result <- kbl( -->
<!--     results_data, -->
<!--    # caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\pha1=-1000$ , #$H_{\\Gamma_{\\text{SAR}}}=2.493$."), -->
<!--     format = "latex", -->
<!--     booktabs = TRUE, -->
<!--     align = "c", -->
<!--     escape = FALSE, -->
<!--     digits = 4, -->
<!--     label = "table_hipotesis" -->
<!--   ) %>% -->
<!--     collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle") -->

<!--   cat("### Results for mu =", mu_val, "\n") -->
<!--   print(table_result) -->

<!--   # Interpretación de rechazo o no rechazo -->
<!--   cat(ifelse(nrow(results_data) > 0, -->
<!--              paste("For mu =", mu_val, ":\n"), -->
<!--              paste("No observations for mu =", mu_val, ":\n"))) -->

<!--   cat(ifelse(nrow(results_data) > 0, -->
<!--              paste( -->
<!--                "Sample Size ", results_data$`$n$`, " Estimator ", results_data$Estimator, -->
<!--                ifelse(results_data$RejectNull, -->
<!--                       " the null hypothesis is rejected.", -->
<!--                       " the null hypothesis is not rejected." -->
<!--                ), "\n" -->
<!--              ), -->
<!--              "\n")) -->
<!-- } -->

<!-- ``` -->

### 2024-02-01 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
add size and power analysis and new images

  plot <- ggplot(plot_data$TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = plot_data$TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    annotate("text", x = max(plot_data$TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
             label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
    annotate("text", x = max(plot_data$TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
             label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
    labs(x = "Entropy", y = "Empirical Density") +
    annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

@@

$$
 \begin{cases}\mathcal{H}_0: \mu_{\widetilde{H}}-\mu_{H}=0 \\ 
  \mathcal{H}_1:\mu_{\widetilde{H}}-\mu_{H}\neq0 .\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle.

@@

```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 100
mu <- 1
B <- 1
alpha1 <- -8
sample.size <- c(50, 100, 150, 200, 250,300)
L_values <- c(2, 5, 8, 18)

@@

    for (r in 1:R) {
      z <- gamma_sar_sample(L, mu, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
    }

@@

# LaTeX notation for negative numbers and integers
combined_summary_stats[] <- lapply(combined_summary_stats, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

@@

Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using statistical test \eqref{Eq:test_e}. Under the null hypothesis, we observe that the densities are centered around zero. Conversely, under the alternative hypothesis, such as for $\alpha=8$, the density is not centered around zero. It reveals the difference between the entropy of Gamma SAR and $G_I^0$, indicating that we are in a scenario of heterogeneous clutter.

```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}

@@

alpha1_values <- c( -8)

@@

      z <- gamma_sar_sample(L, mu, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      z1 <- gi0_sample(mu, alpha1, L, s)
      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z1, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
        #(L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))

@@

    mean_entropy1[sample.size == s] <- mean(TestStat1)
   # cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")

    mean_entropy2[sample.size == s] <- mean(TestStat2)
   # cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")

@@

  max_density1 <- max(density(TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
  max_density2 <- max(density(TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)

  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )+
    labs(x = "Test Statistics", y = "Density")

@@

To assess the practical efficacy of the proposed test, we conducted experiments using real SAR images acquired by the Sentinel-1A system operating in the C band,with  HH polarization, and intensity format. The set of four SAR images, depicted in Fig.&nbsp;\ref{fig:Real_SAR_Images}(a)-(d) represent diverse scenes: a forested area in the Amazonas region, agricultural fields in Flevoland, and urban areas in Berlin and Ottawa, each with sizes of $512 \times 512$ pixels.

@@

@@

```{r SAR_simulations, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")
x_Brazil <- myread.ENVI(file='../../../Data/SAR/Brazil/Intensity_VV.img', headerfile='../../../Data/SAR/Brazil/Intensity_VV.hdr')
x_Berlin<- myread.ENVI(file='../../../Data/SAR/Berlin/Intensity_VV.img', headerfile='../../../Data/SAR/Berlin/Intensity_VV.hdr')
x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')
x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')

>>>>

  plot <- ggplot(plot_data$TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = plot_data$TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    annotate("text", x = max(plot_data$TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
             label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
    annotate("text", x = max(plot_data$TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
             label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
    labs(x = "Entropy", y = "Density") +
    annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

@@

$$
 \begin{cases}\mathcal{H}_0: \widetilde{H}(\bm{Z})-H(\bm{Z})=0 \\ 
  \mathcal{H}_1:\widetilde{H}(\bm{Z})-H(\bm{Z})\neq0 .\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle.

@@

```{r Simulated_density, echo=FALSE, message=FALSE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 500
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 150)
L_values <- c(2, 5, 8, 18)

@@

    for (r in 1:R) {
      z <- gamma_sar_sample(L, mu, s)
      #z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
    }

@@

# LaTeX notation 
combined_summary_stats[] <- lapply(combined_summary_stats, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

@@

We proceeded to explore the capabilities of the proposed test in terms of size and power. Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2))$, and therefore, the $p$-value of the observed test statistic is $2(1-\Phi(\varepsilon))$, where $\Phi$ is the standard Gaussian cumulative distribution function and 
$$
\varepsilon=\frac{\tilde{H}(\bm{Z})-H(\bm{Z})}{\sigma_S}.
$$
Nominal levels of $1\%$, $5\%$, and $10\%$ were considered. In reference to the size, $1000$ simulations have been used for various sample sizes with  satisfactory results. In all cases, the nominal level has been achieved. The power, in general, improves with the increase in the number of looks. The results are presented in Table \ref{tab:table_size_power}, providing a more detailed insight into the effectiveness of the test under different conditions.

```{r Simulated_power, echo=FALSE, message=FALSE}

# Function to calculate p-value
calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
  epsilon <- test_statistic  / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value)
}

# Function to calculate Type II Error Rate
calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
  return(type_II_error_rate)
}

# Function to calculate power for different L values and alpha_nominals
calculate_power <- function(R, mu, L_values, B, sample_sizes, alpha_nominals) {
  results <- data.frame()

  for (L in L_values) {
    for (alpha_nominal in alpha_nominals) {
      TestStatistics <- list()
      mean_entropy <- numeric(length(sample_sizes))
      sd_entropy <- numeric(length(sample_sizes))

      for (s in sample_sizes) {
        TestStat <- numeric(R)

        for (r in 1:R) {
          z <- gi0_sample(mu, -8, L, s)
          TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
        }

        mean_entropy[sample_sizes == s] <- mean(TestStat)
        sd_entropy[sample_sizes == s] <- sd(TestStat)

        TestStatistics[[as.character(s)]] <- TestStat
      }

      mu_W <-  mean_entropy  
      sigma_W <- sqrt(sd_entropy^2)

      p_values <- lapply(TestStatistics, function(TestStat) {
        apply(data.frame("Test_Statistics" = TestStat), 1, function(row) {
          calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
        })
      })

      type_II_error_rates <- sapply(p_values, function(p_values_for_size) {
        calculate_type_II_error_rate(p_values_for_size, alpha_nominal)
      })

      power <- 1 - type_II_error_rates

      result_row <- data.frame(
        L = L,
        alpha_nominal = alpha_nominal,
        Sample_Size = sample_sizes,
        power = power
      )

      results <- rbind(results, result_row)
    }
  }

  return(results)
}

R <- 500
mu <- 1
L_values <- c(2, 5, 8, 18)
B <- 3
sample_sizes <- c(50, 100, 200, 300)
alpha_nominals <- c(0.01, 0.05, 0.1)

results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
save(results_power, file = "./Data/results_power.Rdata")

```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

# Function to calculate p-value
calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
  epsilon <- test_statistic / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value < alpha_nominal)  # Return TRUE if p_value is less than alpha_nominal
}

R <- 500
mu <- 1
B <- 3
L_values <- c(2, 5, 8, 18)
sample_sizes <- c( 50, 100, 200, 300)
alpha_nominals <- c(0.01, 0.05, 0.1)

results <- data.frame()

for (L in L_values) {
  for (alpha_nominal in alpha_nominals) {
    TestStatistics <- NULL
    mean_entropy <- numeric(length(sample_sizes))
    sd_entropy <- numeric(length(sample_sizes))

    for (s in sample_sizes) {
      TestStat <- numeric(R)

      for (r in 1:R) {
        z <- gamma_sar_sample(L, mu, s)
        TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      }
      mean_entropy[sample_sizes == s] <- mean(TestStat)
      sd_entropy[sample_sizes == s] <- sd(TestStat)

      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
    }

    mu_W <- mean_entropy
    sigma_W <- sqrt(sd_entropy^2)

    p_values <- apply(TestStatistics, 1, function(row) {
      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
    })

    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
    results <- rbind(results, result)
  }
}

save(results, file = "./Data/type_I_results.Rdata")

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
cat("\\setlength{\\tabcolsep}{4pt}\n")
# Load Type I Error Rates
load("./Data/type_I_results.Rdata")

type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
  sum(p_values) / length(p_values)  
})

type_I_error_results <- as.data.frame(as.table(type_I_error_rates))

colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")

spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)

spread_results <- spread_results %>% 
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)

load("./Data/results_power.Rdata")

summary_stats <- results_power %>%
  spread(key = alpha_nominal, value = power) %>%
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)

# Combine the two datasets based on L and sample size
combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
combined_results <- combined_results %>% 
  arrange(L, Sample_Size)
# Reorder the columns
combined_results <- combined_results %>% 
  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)

# Rename columns
colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")

# LaTeX notation 
combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

# Print the combined table
table_combined_result <- kbl(
  combined_results,
  caption = "Size and Power of the proposed test.",
  format = "latex",
  booktabs = TRUE,
  align = "lcccccccc",
  escape = FALSE,
  digits = 3,
  label = "table_size_power"
)%>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")

print(table_combined_result)

Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using statistical test \eqref{Eq:test_e}. Under the null hypothesis, we observe that the densities are centered around zero. Conversely, under the alternative hypothesis, such as for $\alpha=-8$, the density is not centered around zero. It reveals the difference between the entropy of Gamma SAR and $G_I^0$, indicating that we are in a scenario of heterogeneous clutter.

```{r Sim_empirical_test, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}

@@

alpha1_values <- c( -2)

@@

      z <- gamma_sar_sample(L, mu, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      z1 <- gi0_sample(mu, alpha1, L, s)
      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z1, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))

@@

    TestStatistics1 <- rbind(TestStatistics1, data.frame("Sample_Size" = rep(s, R), "Test_Statistics" = TestStat1))
    TestStatistics2 <- rbind(TestStatistics2, data.frame("Sample_Size2" = rep(s, R), "Test_Statistics2" = TestStat2))
  }
}

# 
save(TestStatistics1, TestStatistics2, file = "./Data/sim_empirical_test.Rdata")

```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}

# 
load("./Data/sim_empirical_test.Rdata")

@@

for (alpha_val in alpha1_values) {
  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )+
    labs(x = "Test Statistics", y = "Density")

@@

To assess the practical efficacy of the proposed test, we conducted experiments using real SAR images acquired by the Sentinel-1A system operating in the C band, with  HH polarization, and intensity format. The set of four SAR images, depicted in Fig.&nbsp;\ref{fig:Real_SAR_Images}(a)-(d) represent diverse scenes: a forested area in the Amazonas region, agricultural fields in Flevoland, and urban areas in Berlin and Ottawa, each with sizes of $512 \times 512$ pixels.

@@

```{r window, fig.align="center",  out.width = "80%", fig.cap=" Sketch of sliding window.", fig.show="hold",  fig.pos="hbt"}
knitr::include_graphics("../../../Figures/PDF/sliding2.pdf")
```

@@

```{r SAR_simulations, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")
x_Brazil <- myread.ENVI(file='../../../Data/SAR/Brazil/Intensity_VV.img', headerfile='../../../Data/SAR/Brazil/Intensity_VV.hdr')
x_Berlin<- myread.ENVI(file='../../../Data/SAR/Berlin/Intensity_VV.img', headerfile='../../../Data/SAR/Berlin/Intensity_VV.hdr')
x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')

x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland2/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland2/Intensity_VV.hdr')
x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
